---
title: "Models_vac_project"
author: "Mary M Barker"
date: "08/12/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load R packages
```{r}
library(tidyverse)
library(haven)
library(dplyr)
library(tidymodels)
library(broom)
library(broom.mixed)
library(glue)
library(sandwich)
```

##Load data
```{r}
setwd("data_stata/")
vac <- read_dta("vacc_project_analysis.dta")
```

## Outcomes (all coded as No(0) Yes(1) Missing(2)):
Uptake of at least 1 COVID-19 vaccine by 18th Feb 2022 - "vac_feb"
Uptake of at least 1 COVID-19 vaccine by 30th Sep 2021 - "vac_sep"
Uptake of second dose of COVID19 vaccine by 18th Feb 2022 - "vac_dose2"

## Exposures (all coded as No(0) Yes(1) Missing(2)):
Mental health diagnosis - "ment_dis"
Anxiety - "anx"
Depression - "dep"
Any physical condition - "chronic_phy"
Hypertension - "hypertension"
Heart disease - "heart_dis"
Lung disease - "lung_dis"
Chronic renal failure - "ren_fail"
Cancer - "cancer"
Diabetes - "diab"
Immunological conditions - "immune dis"

## Covariates
Age - "age" (continuous)
Sex - "sex" (coded as Female(0), Male(1), Missing (2))
Previous COVID-19 - "prev_covid" (coded as No(0), Yes(1))
Smoking status - "smoke" (coded as No(0), Yes(1), Missing(2))

## Recode all missing values to NA
```{r}
vac <- vac %>% 
  mutate(across(.cols = c("ment_dis","anx", "dep", "chronic_phy", "hypertension", "heart_dis", "lung_dis", "ren_fail", "cancer", "diab", "immune_dis", "vac_feb", "vac_sep", "vac_dose2", "sex", "smoke", "min2_comorbs"), 
                .fns = ~ ifelse(. == 2, NA, .)))
```

## Create interaction variable
```{r}
vac <- vac %>% 
  mutate(interaction = ment_dis * chronic_phy)  
```


## Create function to define which model results we require
```{r}
get_res <- function(m) {
  df <- tidy(m)
  df$n_obs <- nobs(m)
  df
}
```

## Define model specifications
```{r}
outcomes <- c("vac_feb", "vac_sep", "vac_dose2")
exposures <- c("ment_dis","anx", "dep", "chronic_phy", "hypertension", "heart_dis", "lung_dis", "ren_fail", "cancer", "diab", "immune_dis")
adjustments <- c("age + sex", "age + sex + prev_covid", "age + sex + prev_covid + smoke + min2_comorbs", "age + sex + prev_covid + smoke + min2_comorbs + interaction")
spec <- expand.grid(outcomes, exposures, adjustments)
spec$ID_real <- as.character(1:132)
formulas <- glue("{spec$Var1} ~ {spec$Var2} + {spec$Var3}")
```

## Run models and save results to data frame
```{r}
robust_se <- function(model) {
  sqrt(diag(sandwich(model)))
}
res <- map(formulas, ~ glm(., data = vac,
                           family = poisson(link = log))) %>%
  map_dfr(~ cbind(tidy(.), robust_se = robust_se(.))) %>%
  mutate(RR = exp(estimate), Lower = exp(estimate - 1.96 * robust_se), Higher = exp(estimate + 1.96 * robust_se))
```

## Save model results data frame as a .csv file
```{r}
write.table(res, file = "Tables/vac_mod_results_ver3.csv", sep = ",", 
            row.names = FALSE, col.names = TRUE, quote=FALSE)
```